The pragmatics of perspective-taking

### 2018-03-26 writing/journal_manuscript/manuscript.tex
Minor revisions

Second, because half of the instructions were unscripted, we were able to observe natural production of referential descriptions for a number of fillers. Informally, we noted a tendency toward over-informativity. Instead of ``move the stuffed animal down'', they'll say ``move the stuffed pa'nda bear down.'' Or, instead of saying ``move the plane to the right,'' they'll say ``move the red airplane to the right,'' even though there is only one plane. This suggested that the confederate's scripted instructions were in some sense uncooperative and counter to the matcher's expectations. Perhaps directors were taking the time to make more costly over-informative descriptions because they believed it was contextually relevant: both parties know that there are hidden objects in the environment. If the matcher reasoned in this way and expected the director to be overinformative, then they would be justified in picking the first object that meets the description rather than worrying about occluded cells. We tested this prediction in Exp.~2, where we removed the scripted instructions and allowed speakers to refer to items however they wished. If speakers really are being overinformative, and listeners are correctly expecting this, we should see fewer errors after removing uncooperative scripts.

@@

%consider the speaker's communicative goals and context. 
In our replication, we found evidence that listeners neglect the speaker's epistemic state, as Keysar and colleagues claim.
We also found that when the speaker's utterance fit the hidden distractor better than the target, matchers were more likely to make errors. 
Indeed, we found that the extremely heterogeneous pattern of errors across items was well explained by the relative fit of the utterance to target and distractor.
This suggests that reference disambiguation was driven primarily by \emph{a priori} label fitness rather than consideration of occluded vs. mutual visible items. 
%
However, this does not necessarily imply limitations on theory of mind---if speakers could be expected to naturally provide expressions which apply better to the target, then this behavior would be appropriate.
% If listeners arrive at this interpretation strategy through pragmatic reasoning, then neglecting the speaker's epistemic state would be rational and also the result of theory of mind use. 
In Expt.~2, we found that speakers did naturally produce more precise, informative utterances than required and these unconstrained utterances fit the target significantly better than they fit the hidden distractor. 
For example, no speaker in Expt.~2 produced ``the bottom block,'' which was used as a critical instruction in Expt.~1. Instead, they said ``the bluish block with a B'' or ``block with the blue writing,'' which relied on less confusable perceptual features and thereby decreased error rates. 
Thus, the errors observed in Expt.~1 can be explained as a result of an uncooperative confederate (speaker)---the experiment set up certain pragmatic expectations through the task context, then deliberately flouted them in critical trials.

The Gricean maxim of quality dictates that cooperative speakers should make their utterance as informative as is required for current purposes, but no more so. If the referring expressions used in Expt.~1 uniquely pick out the target from the speaker's perspective, then why would unscripted speakers in Expt.~2 be more informative than this? 
%strictly necessary and why would listeners come to expect such ``overinformativity''? 
One possibility is that awareness of the complex mismatch in epistemic state with the listener leads the speaker to provide extra information in an attempt to avoid miscommunication.
Another possibility is that more general dynamics of language are in play.
Studies of over-informativity in referring expressions have uncovered a general tendency of speakers to provide redundant information.
This tendency can depend on a number of situational factors, such as the tendency to mention perceptually salient features to speed up the identification process  \cite{KoolenGattGoudbeekKrahmer11_Overspecification}. 
%In the current task, it seems particularly relevant that both participants knew about the presence of hidden objects, increasing uncertainty about possible distractors and placing additional pressure on the speaker to overspecify. 
The exact origin is a subject that must be followed up by future research \cite[e.g.]{GannBarr14_AudienceDesign}, but it is clear that the tendency of speakers to produce highly informative referring expressions is useful to, and relied on by, listeners. 
%Indeed, the remaining errors in Expt.~2 are at least partially due to the lack of availability of more specific expressions. 
%The items on which errors were most likely in Expt.~2 were difficult precisely because the natural utterance was \emph{still} ambiguous: even if the speaker uses ``hairbrush'' instead of the basic-level ``brush,'' for example, the distractor remains a more typical exemplar of the subcategory.

>>>>

%Second, because half of the instructions were unscripted, we were able to observe natural production of referential descriptions for a number of fillers. Informally, we noted a tendency toward over-informativity. Instead of ``move the stuffed animal down'', they'll say ``move the stuffed pa'nda bear down.'' Or, instead of saying ``move the plane to the right,'' they'll say ``move the red airplane to the right,'' even though there is only one plane. This suggested that the confederate's scripted instructions were in some sense uncooperative and counter to the matcher's expectations. Perhaps directors were taking the time to make more costly over-informative descriptions because they believed it was contextually relevant: both parties know that there are hidden objects in the environment. If the matcher reasoned in this way and expected the director to be overinformative, then they would be justified in picking the first object that meets the description rather than worrying about occluded cells. We tested this prediction in Exp.~2, where we removed the scripted instructions and allowed speakers to refer to items however they wished. If speakers really are being overinformative, and listeners are correctly expecting this, we should see fewer errors after removing uncooperative scripts.

@@

% 
In our replication, we found empirical support for the claim that listeners neglect the speaker's epistemic state in some contexts, as claimed by \cite{KeysarLinBarr03_LimitsOnTheoryOfMindUse}: when the speaker's utterance fit the hidden distractor better than the target, matchers were more likely to make errors. 
Indeed, we found that the extremely heterogeneous pattern of errors across items was well explained by the relative fit of the utterance to target and distractor.
This suggests that reference disambiguation was driven primarily by \emph{a priori} label fitness rather than consideration of occluded vs. mutually visible items.

However, this finding does \emph{not} necessarily imply limitations on theory of mind. Speakers systematically provide more informative utterances in contexts where views are uncertain, hence listeners with well-calibrated social expectations are justified in neglecting perspective. Rather than debating provide a principled, rational explanation of \emph{why} listeners may neglect speaker perspective in the first place. These reasons stem from more sophisticated pragmatic expectations than simple consideration of perspective, thereby opening a deeper avenue by which theory of mind use guides flexible communication. % if speakers could be expected to naturally provide expressions which apply better to the target, then this behavior would be appropriate.
% If listeners arrive at this interpretation strategy through pragmatic reasoning, then neglecting the speaker's epistemic state would be rational and also the result of theory of mind use.

%We found that speakers did naturally produce more precise, informative utterances than required and these unconstrained utterances fit the target significantly better than they fit the hidden distractor. 
%For example, no speaker in Expt.~2 produced ``the bottom block,'' which was used as a critical instruction in Expt.~1. Instead, they said ``the bluish block with a B'' or ``block with the blue writing,'' which relied on less confusable perceptual features and thereby decreased error rates. 
%Thus, the errors observed in Expt.~1 can be explained as a result of an uncooperative confederate (speaker)---the experiment set up certain pragmatic expectations through the task context, then deliberately flouted them in critical trials.

%%%%%%%
% Discussion points:

% 1. Tying back to original expt (e.g. pitch Expt. 3 idea). Listeners didn't know what's going on when they heard the dramatically under-informative `tape' -- one direction for future work is to directly manipulate expectations about speakers...

% 2. Other reasons for over-informativity (e.g. Judith stuff)

% 3. Relationship to Heller model, Rubio-Fernandez, other critiques of Keysar?

% 4. 
%%%%%%%

The Gricean maxim of quality dictates that cooperative speakers should make their utterance as informative as is required for current purposes, but no more so. If the referring expressions used in by confederates uniquely pick out the target from the speaker's perspective, then why our unscripted speakers be more informative than this? 
%strictly necessary and why would listeners come to expect such ``overinformativity''? 
One possibility, which we tested in Exp. 2, is that awareness of the complex mismatch in epistemic state with the listener leads the speaker to provide extra information in an attempt to avoid miscommunication.
Another possibility is that more general dynamics of language are in play.
Studies of over-informativity in referring expressions have uncovered a general tendency of speakers to provide redundant information.
This tendency can depend on a number of situational factors, such as the tendency to mention perceptually salient features to speed up the identification process  \cite{KoolenGattGoudbeekKrahmer11_Overspecification}. 
%In the current task, it seems particularly relevant that both participants knew about the presence of hidden objects, increasing uncertainty about possible distractors and placing additional pressure on the speaker to overspecify. 
The exact origin is a subject that must be followed up by future research \cite[e.g.]{GannBarr14_AudienceDesign}, but it is clear that the tendency of speakers to produce highly informative referring expressions is useful to, and relied on by, listeners. 
%Indeed, the remaining errors in Expt.~2 are at least partially due to the lack of availability of more specific expressions. 
%The items on which errors were most likely in Expt.~2 were difficult precisely because the natural utterance was \emph{still} ambiguous: even if the speaker uses ``hairbrush'' instead of the basic-level ``brush,'' for example, the distractor remains a more typical exemplar of the subcategory.
